Minimizing post-shock forecasting error using disparate information

### 2020-06-09 manuscript/fig2.tex
addition of more references to introduction, error fixing in dataanalysis. R(not adjust for inflation for 2008-Sep time series), and other updates in the manuscript (see 1st page)

% Created by tikzDevice version 0.12.3 on 2020-06-05 08:57:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.63) --
	(481.73, 87.05) --
	(476.44, 87.05) --
	(479.09, 91.63);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 91.18) -- (481.86, 91.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 88.41) -- (479.09, 93.96);
\definecolor{drawColor}{RGB}{238,99,99}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-06-09 17:22:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.16) --
	(481.73, 86.58) --
	(476.44, 86.58) --
	(479.09, 91.16);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 87.98) -- (481.86, 87.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.20) -- (479.09, 90.75);
\definecolor{drawColor}{RGB}{238,99,99}
